Dual selection games

### 2018-07-15 articles/dual-selection-games/article.tex
add abstract, define dual

\begin{abstract}
  (an investigation of dual selection games)
\end{abstract}

@@

\begin{definition}
  For a set \(X\), let \(\mathbf C(X)\) be the collection of all
  choice functions on \(X\), functions \(f:X\to\bigcup X\) 
  such that \(f(x)\in x\) for all \(x\in X\).
\end{definition}

@@

  For example, a reflection of the collection \(\mc O_X\) of basic open covers
  of \(X\) would be \(\mc P_X=\{\mc T_{X,x}:x\in X\}\), where \(\mc T_{X,x}\) 
  is the corresponding point-base at \(x\in X\). 
  Likewise for the collection \(\Omega_{X,x}\)
  of sets with \(x\in X\) as a limit point, \(\mc T_{X,x}\) is itself
  a reflection.

\begin{lemma}
  Let \(\mc R\) be a reflection of \(\mc A\). Then \(\bigcup \mc R=\bigcup \mc A\).
\end{lemma}
\begin{proof}
  If \(x\in \bigcup\mc A\), then \(x\in\ran{f}\) for some \(f\in\mathbf C(\mc R)\).
  Thus \(x=f(R)\in R\) for some \(R\in\mc R\), showing \(x\in\bigcup\mc R\).

@@

@@

  So choose \(\tau(n)\in\mc R\) such that for all \(r\in \tau(n)\)
  there exists \(A_{r,n}\in\mc A\) such that \(\sigma(A_{r,n},n)=r\).
  It follows that when \(r_n\in\tau(n)\) for \(n<\omega\),
  \(\{r_n:n<\omega\}=\{\sigma(A_{r_n,n}:n<\omega\}\in B\),
  so \(\tau\) witnesses
  \(\plI\prewin\schStrongSelGame{\mc R}{\neg\mc B}\).

@@

@@

>>>>

\begin{abstract}
  Often, selection games have dual games for which a winning
  strategy for a player in one game may be used to create
  a winning strategy 
  For example, the Rothberger selection game involving open covers
  is dual to the point-open game. This extends to a general
  theorem: if \(\mc A=\{\ran{f}:f\in\mathbf C(\mc R)\}\)
  where \(\mathbf C(\mc R)=\{f\in(\bigcup\mc R)^{\mc R}:R\in\mc R\Rightarrow f(R)\in R\}\) 
  collects the choice functions on the set \(\mc R\),
  then \(G_1(\mc A,\mc B)\) and \(G_1(\mc R,\neg\mc B)\)
  are dual selection games. 
\end{abstract}

@@

\begin{definition}
  For a set \(X\), let \(\mathbf C(X)=\{f\in(\bigcup X)^X:x\in X\Rightarrow f(x)\in x\}\)
  be the collection of all choice functions on \(X\).
\end{definition}

@@

As we will see, reflections of selection sets are used frequently (but implicitly) 
throughout the literature to define dual selection games.

%  For example, a reflection of the collection \(\mc O_X\) of basic open covers
%  of \(X\) would be \(\mc P_X=\{\mc T_{X,x}:x\in X\}\), where \(\mc T_{X,x}\) 
%  is the corresponding point-base at \(x\in X\). 
%  Likewise for the collection \(\Omega_{X,x}\)
%  of sets with \(x\in X\) as a limit point, \(\mc T_{X,x}\) is itself
%  a reflection.

\section{Main Results}

\begin{proposition}
  Let \(\mc R\) be a reflection of \(\mc A\). Then \(\bigcup \mc R=\bigcup \mc A\).
\end{proposition}
\begin{proof}
  If \(x\in \bigcup\mc A\), then \(x\in\ran{f}\) for some \(f\in\mathbf C(\mc R)\).
  Thus \(x=f(R)\in R\) for some \(R\in\mc R\), showing \(x\in\bigcup\mc R\).

@@

The following four theorems demonstrate that reflections characterize
dual selection games for both perfect information strategies and
certain limited information strategies.

\begin{definition}
  A pair of games \(G(X),H(X)\) are \term{Markov information dual} if both
  of the following hold.
  \begin{itemize}
    \item \(I\prewin G(X)\) if and only if \(II\markwin H(X)\).
    \item \(II\markwin G(X)\) if and only if \(I\prewin H(X)\).
  \end{itemize}
\end{definition}

@@

  So choose \(\tau(n)\in\mc R\) such that for all \(r\in \tau(n)\)
  there exists \(A_{r,n}\in\mc A\) such that \(\sigma(A_{r,n},n)=r\).
  It follows that when \(r_n\in\tau(n)\) for \(n<\omega\),
  \(\{r_n:n<\omega\}=\{\sigma(A_{r_n,n}):n<\omega\}\in B\),
  so \(\tau\) witnesses
  \(\plI\prewin\schStrongSelGame{\mc R}{\neg\mc B}\).

@@

\begin{definition}
  A pair of games \(G(X),H(X)\) are \term{perfect information dual} if both
  of the following hold.
  \begin{itemize}
    \item \(I\win G(X)\) if and only if \(II\win H(X)\).
    \item \(II\win G(X)\) if and only if \(I\win H(X)\).
  \end{itemize}
\end{definition}

@@

\begin{corollary}
  If \(\mc R\) is a reflection of \(\mc A\),
  then \(\schStrongSelGame{\mc A}{\mc B}\) and \(\schStrongSelGame{\mc R}{\neg\mc B}\)
  are both perfect information dual and Markov information dual.
\end{corollary}
